---
title: "Final Project"
output: html_document
---

Makai Freeman 115153547
Brian Murray 114120922


# Introduction

This is a tutorial created for our final project for CMSC320 at the University of Maryland. This tutorial is a walkthrough the data science pipeline. This includes data curation, parsing, and management; exploratory data analysis; hypothesis testing and machine learning to provide analysis; and the curation of a message covering insights learned during the tutorial. 

To complete this tutorial, we use listings from Airbnb in the Washington D.C. area. The ultimate goal is to use the pipeline mentioned above to predict the cost of future listings in the area.  

First we need some packages. 
###### NEED TO ADD THE PACKAGES THAT WE USE AND A SHORT DESCRUPTION #########

```{r load_data, message=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
```

# 1. Data Curation, Parsing, and Management

First we want to find suitable data, we used data straight from Airbnb. 
Then we want to download the data from the website. This is done using the "read_csv" function as the file we want to download is a csv (Comma-separated values).
```{r load data, message=FALSE}
abnb <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2019-04-15/visualisations/listings.csv")

head(abnb)
```
This downloads the data and stores it as a tibble with the name "abnb."

Next we want to take this data and manipulate it a bit. To do this, we want to remove the values that we will not need. In our case, it is the columns "neighbourhood_group", "last_review", and "reviews_per_month."

We will use the functions 
select()
%>%

```{r convert}

abnb <- abnb %>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")

head(abnb)
```

This takes the previous tibble and removes the columns that we will not be using. 


```{r days}

abnb %>% 
  ggplot(aes(x = '', y = availability_365)) + geom_boxplot()

```

This plot shows the spread of available days in the next year for the listings included in the dataset. The listings have anywhere from 0 to 365 days available, with the mean appearing to be around 80. 


```{r neighborhoods}

abnb %>% 
  ggplot(aes(x = neighbourhood)) + geom_histogram(stat="count")

```
This plot shows the number of listings that are in each neighborhood in Washington, D.C. _____ has the most listings with almost 875. 

```{r price}

abnb %>% 
  ggplot(aes(x = '', y = price)) + geom_boxplot()

```
This plot shows the spread of prices for Washington D.C. listings. 


```{r min_nights}

abnb %>% 
  ggplot(aes(x = '', y = minimum_nights)) + geom_boxplot()

```
This graph shows the spread of minimum number of nights required by listings in Washington D.C.

```{r num listings}

abnb %>% 
  select(host_id, calculated_host_listings_count) %>%
  unique() %>%
  ggplot(aes(x = calculated_host_listings_count)) + geom_histogram()

```
This plot shows the number of hosts with a given number of listings.





