---
title: "Final Project"
output: html_document
---

Makai Freeman 115153547

Brian Murray 114120922

Chukwuemeka Okeke 114585332

# Introduction

This is a tutorial created for our final project for CMSC320 (Introduction to Data Science) at the University of Maryland. This tutorial is a walkthrough of the data science pipeline. This includes data curation, parsing, and management; exploratory data analysis; hypothesis testing and machine learning to provide analysis; and the curation of a message covering insights learned during the tutorial. 

To complete this tutorial, we use listings from Airbnb in the Washington D.C. area. The ultimate goal is to use the pipeline mentioned above to predict the cost of future listings in the area.  

First we need some packages. 
readr - contains methods used to read rectangular data like csv files (doumentation can be found at https://readr.tidyverse.org/)

dplyr - contains methods used to manipulate data frames (documentation can be found at https://dplyr.tidyverse.org)

tidyverse - contains packages commonly used in data analysis (documentation can be found at https://www.tidyverse.org/packages/)

leaflet - contains methods used to create interactive maps (documentation can be found at https://rstudio.github.io/leaflet/)

```{r load_data, message=FALSE}
library(readr)
library(dplyr)
library(tidyverse)
library(leaflet)
library(broom)
```

# 1. Data Curation, Parsing, and Management

First we want to find suitable data, we used data straight from Airbnb. 
Then we want to download the data from the website. This is done using the "read_csv" function as the file we want to download is a csv (Comma-separated values).
```{r load data, message=FALSE}
abnb <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2019-04-15/visualisations/listings.csv")

head(abnb)
```

This downloads the data and stores it as a tibble with the name "abnb."

Next we want to take this data and manipulate it a bit. To do this, we want to remove the values that we will not need. In our case, it is the columns "neighbourhood_group", "last_review", and "reviews_per_month."

We will use the functions 
select() - Chooses columns of a dataframe to keep
%>% - Creates a pipeline to use with a dataframe

```{r convert}
#remove unwanted columns
abnb <- abnb %>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")

head(abnb)
```

This takes the previous tibble and removes the columns that we will not be using. 


# 2. Exploratory Data Analysis
Next we move into exploratory data analysis. Exploratory data analysis is the investigation of variables across observations. We want to spot any issues with our data, explore variable properties, and look at possible models for our data. 



We will begin with a display of each distribution for our variables. 

To do this, we use a few new functions:

ggplot() - begins a plot that you have to add layers to
      related geom functions:
      
      geom_histogram() - creates histogram
      
      geom_bar() - creates a bar graph
      
      geom_violin() - creates a violin graph
      
      geom_point() - creates a scatterplot

group_by() - allows operations to be performed by the group of a certain column

summarize() - produces summary statistics for data frames

labs() - specifies the labels used onthe axes of a plot

coord_flip() - swaps the x and y axes

scale_x/y_log10() - performs a logarithmic scaling of the values on the x/y axis

# Part A

For the first part of our data analysis, we will be looking at the spread and concentration of individual variables.

```{r availability}
#creates histogram with bins that have a range of 50
abnb %>%
  ggplot(aes(x = availability_365)) +
  geom_histogram(binwidth = 50)
```

This histogram explores the number of days each listing is available. The possible values are from 0-365. Since we only want listings that are available we will remove all of the listings that have 0 days available and replot. 


```{r availability remove 0}  
# updates the variable so the availability is at least 1 day
abnb <- abnb[abnb$availability_365 > 0,]

abnb %>%
  ggplot(aes(x = availability_365)) +
  geom_histogram(binwidth = 50)

```

This plot is more even than before. The data seems to be bimodal with peaks around 50-100 and 300+. The latter makes sense as there are likely many locations that are available 365 days a year.

```{r neighborhoods}
#counts the number of listings in each neighborhood and order them from least to greatest count
abnb %>%
  group_by(neighbourhood) %>%
  summarize(neigh_count = n()) %>%
  ggplot(aes(x=reorder(neighbourhood, -neigh_count), y=neigh_count)) +
  geom_bar(stat = "identity") +
  labs(x="Neighborhood", y="Count") +
  coord_flip() 
```

This plot shows the number of listings that are in each neighborhood in Washington, D.C.. Capitol Hill, Lincoln Park has the most listings with 610. 

```{r price}
abnb %>% 
  ggplot(aes(x = price)) + 
  geom_histogram(bins = 100) +
  scale_x_log10()
```

This plot shows the spread of prices for Washington D.C. listings. We use a logarithmic scale for this because there is a huge outlier as one listing has a price of $10,000. This graph is skewed right but has a median around 100-200 dollars.


```{r min_nights}

abnb %>% 
  ggplot(aes(x = minimum_nights)) + 
  geom_histogram(binwidth = .25) +
  scale_x_log10()

```

This graph shows the spread of minimum number of nights required by listings in Washington D.C.. We also use a logorithmic scale as there is an outlier at over 600 minimum nights. 


# Part B

For the second part of our data analysis, we will be looking at one variable in terms of another, in this case price by room type and price by neighborhood.

```{r price by room}
#create a violin plot 
abnb %>%
  ggplot(aes(x= room_type, y = price)) +
  geom_violin(draw_quantiles = .5) +
  scale_y_log10()

```

This plot is a violin plot with the median drawn as a horizontal line. From this plot we can see a possible correlation between price and type of room.

```{r neighborhood price}
#caluclates the median price per night in each neighborhood and orders them from least to greatest
abnb %>%
  group_by(neighbourhood) %>%
  summarize(neigh_med = median(price)) %>%
  ggplot(aes(x=reorder(neighbourhood, -neigh_med), y=neigh_med)) +
  geom_point() +
  labs(x="Neighborhood", y="Price per Night") +
  coord_flip() 
```
This plot shows the median price per night in each neighborhood. We can see that the West End, Foggy Bottom, GWU neighborhood has the highest median price per night.   

# 3. Hypothesis testing

As we continue with our analysis, we are going to need more data to make predictions about the future of these listings on Airbnb. Our current data was collected in April 2019, we will add data that was compiled between April 2018 and April 2019 in order to look at changes over time so that we can make predictions about the future. 

We will also use the data that is previously compiled to decide if neighborhood has an affect on price. 

New functions:
as.Date() - takes a string and turns it into a datetime object
rbind() - concatinates dataframes with the same columns
arrange() - sorts data from least to greatest by a column value
geom_smooth() - plots a line of best fit to a graph
aov() - performs a one-way ANOVA test
summary() - summarizes the analysis of variance model from aov()
TukeyHSD() - performs a Tukey HSD test
slice() - selects rows by position

```{r load new data, message=FALSE}
#adds date column to current dataframe for identification
abnb$date_compiled <- as.Date("2019-04-01")

#downloads and reformats the available data for the year April 2018 - April 2019
a18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-04-15/visualisations/listings.csv") %>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
a18$date_compiled <- as.Date("2018-04-01")

m18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-05-18/visualisations/listings.csv") %>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
m18$date_compiled <- as.Date("2018-05-01")

j18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-07-20/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
j18$date_compiled <- as.Date("2018-07-01")

aug18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-08-18/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
aug18$date_compiled <- as.Date("2018-08-01")

s18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-09-14/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
s18$date_compiled <- as.Date("2018-09-01")

o18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-10-12/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
o18$date_compiled <- as.Date("2018-10-01")

n18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-11-15/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
n18$date_compiled <- as.Date("2018-11-01")

d18 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2018-12-13/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
d18$date_compiled <- as.Date("2018-12-01")

j19 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2019-01-17/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
j19$date_compiled <- as.Date("2019-01-01")

f19 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2019-02-11/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
f19$date_compiled <- as.Date("2019-02-01")

m19 <- read_csv("http://data.insideairbnb.com/united-states/dc/washington-dc/2019-03-12/visualisations/listings.csv")%>% 
  select(-"neighbourhood_group", -"last_review", -"reviews_per_month")
m19$date_compiled <- as.Date("2019-03-01")


abnb <- rbind(abnb, a18, m18, j18, aug18, s18, o18, n18, d18, j19, f19, m19)
abnb <- abnb[abnb$availability_365 > 0,]
head(abnb)
```



```{r mean price}

abnb %>% 
  arrange(date_compiled) %>%
  group_by(date_compiled) %>%
  summarise(qw = mean(price)) %>%
  ggplot(aes(x = date_compiled, y = qw)) +
  geom_point() +
  geom_smooth(method = lm)
``` 

From this plot, we can see that there seems to be a slight linear relationship between the mean price and the time of year. To confirm this, we will do a hypothesis test on the relationship.

```{r hypo price*date}
#compute analysis of variance
hg <- aov(price ~ date_compiled, data = abnb)
#summarize variance model
summary(hg)

```
The analysis of variance produced a p-value smaller than 0.05.Because of this, we can reject the null hypothesis of no relation for price and the time of year. We will run this test two more times, to see if there is a relationship between room type and price and price and neighborhood. We can see that from our graph above, our inital prediction of a relationship between price and year was correct. 

```{r hypo price * room type}

hg <- aov(price ~ room_type, data = abnb)
summary(hg)
TukeyHSD(hg)

```
From our anaylsis above you can see that we obtained a pvalue lower than 0.05. Hence we rejected our null hypothesis on the affects of room type on the price of the airbnb. 

```{r hypo price * neighborhood}
hg <- aov(price ~ neighbourhood, data = abnb)
summary(hg)
```

When analyzing price when related to neighborhood, we see that the p-value is extremely small thus we reject the null hyopthesis that each neighborhood has the same price. We can again see that from our graph above that there is a relationship between price and the neighborhood that the listing is in. 

#4. Machine Learning

In this section, we will be creating linear models for the price vs time of year and price vs number of listings. 

New functions:

lm() - creates the linear model

tidy() - summarizes linear model in a table

augment() - converts non-tidy data to a data frame

```{r price vs time of year}
#create linear model
lr <- lm(price~date_compiled, data=abnb)

#convert and display results
lr_stat <- lr%>%
  tidy()

head(lr_stat)

#plot residuals
lr%>%
  augment()%>%
  ggplot(aes(x=.fitted, y = .resid))+
  geom_point()+ geom_smooth(method = lm)
```

We are going to reject the null hypothesis of no relationship between the time of year and price. As our p-value shows there is a significant relationship between price and the time of year. As the year reaches fall and winter there is a slight decrease in the price of Airbnbs. 

```{r price vs number of listings}
lr <- lm(price~calculated_host_listings_count, data = abnb)

lr_stats <- lr %>%
  tidy()

head(lr_stats)

lr %>% 
  augment() %>% 
  ggplot(aes(x = .fitted, y = .resid)) + geom_point()
```

Based on the data from this linear model, the number of listings that a host has a relationship with the price that they charge per night. The p-value for the regression model is below the necessary .05 to reject the null hypothesis of no relationship. The plot of the residuals confirms this, with a much larger spread for those with fewer listings. 

#Conclusions

From our data pipleine, we were able to draw a number of conclusions about Airbnb listings in Washington D.C.. We saw that the average price of available listings decreased as the year moved from summer to fall and winter. Hosts that have multiple listings on Airbnb are more likely to have more affordable options, with lower costs per night. We confirmed that the type of room you are booking will affect the price that you pay. These insights could be valuable for people looking to stay in an Airbnb in Washngton D.C.. Knowing that the prices dropped in the latter half of the year may encourage travelers to come to the area in the Fall or Winter as opposed to the Spring or Summer.
 

For further visualization, we decided to include a map with this tutorial. With this map, you can zoom in on a certain area and see the address and nightly price for Airbnbs in Washington, D.C..

```{r map, message=FALSE}

icons <- awesomeIcons(
 # markerColor = getColor(abnb)
)
abnbmap <- leaflet(abnb) %>%
  addTiles() %>%
  addAwesomeMarkers(icon = icons, clusterOptions = markerClusterOptions(), label = ~as.character(name), popup = ~as.character(price)) %>%
   setView(lat=38.9072, lng=-77.0369, zoom=12)
abnbmap
```